Blocking-resistant communication\\through domain fronting

### 2014-07-31 docs/meek.tex
Discussion.

We implemented \meek\ as a pluggable transport~\cite{pt} for Tor.
Although it is possible to use the system with proxies other than Tor,
using Tor has some attractive features.
The pluggable transports infrastructure makes it relatively easy to prototype
a circumvention technique and connect it to a global proxy network.
We can treat confidentiality and integrity of tunneled communication
as a problem solved by Tor, which we don't need to solve separately.
Tor's extra proxy hops mean that the HTTP reflector (App Engine)
and the entry bridge do not have to be trusted.

@@

% Firefox plugin uses normal browser trust store.
% Adversary controls CAs. Can MITM and read your tag and block you.
% Maybe not willing to risk getting caught in MITM.
% Could conceivably send cover traffic if MITM detected, but blah.

@@

\section{Future work}
\label{sec:futurework}

In future work we would like to implement pipelining of requests,
so that more than one HTTP request can be outstanding at a time.
This would have better performance compared to the current system,
which serializes requests and responses in order to keep the
underlying TCP stream in order.
A system of sequence numbers and acknowledgments as used in OSS~\cite{oss}
could make this possible.
% Would be useful for Iran-like session cutoff, independent of \meek.

% Performance measurements
We would like to do more quantitative performance measurements,
in order to measure the overhead in bandwidth and latency that \meek\ has over plain Tor.
We have done informal tests, such as browsing YouTube,
but have not yet put numbers to our measurements.

% Load balancing

>>>>

% We implemented \meek\ as a pluggable transport~\cite{pt} for Tor.
% Although it is possible to use the system with proxies other than Tor,
% using Tor has some attractive features.
% The pluggable transports infrastructure makes it relatively easy to prototype
% a circumvention technique and connect it to a global proxy network.
% We can treat confidentiality and integrity of tunneled communication
% as a problem solved by Tor, which we don't need to solve separately.
% Tor's extra proxy hops mean that the HTTP reflector (App Engine)
% and the entry bridge do not have to be trusted.

The current implementation of meek strictly serializes
its HTTPS requests and responses,
in order to keep the chunks of the underlying TCP stream
in the proper order.
The unfortunate side effect of this simple approach
is delay that gets worse with higher round-trip times.
In future work we plan to add an additional reliability layer,
perhaps like the system of sequence numbers and acknowledgments used in OSS~\cite{oss},
that would allow requests to be pipelined
and cope with out-of-order delivery.
Figure~\ref{fig:wire-sequential} shows the current implementation,
and Figure~\ref{fig:wire-parallel} shows the nature of performance
improvement that could be gained with a reliability layer.
% Would be useful for Iran-like session cutoff, independent of \meek.

@@

meek's use of HTTPS is subject to the usual public key infrastructure
and trust model.
The browser running the HTTPS camouflage extension (Section~\ref{sec:browserextension})
has a standard list of trusted certificate authorities.
A censor that controls a certificate authority trusted by the browser
would be able to do a man-in-the-middle attack
between the client and the intermediate web service,
and detect fronting by decrypting HTTP requests and checking for specific Host headers.
Such a censor would be able to detect circumvention,
but still not read the client's plaintext because of the
additional encryption and authentication of the tunneled Tor layer.
It seems risky for the censor to risk being detected in
ia man-in-the-middle attack merely to confirm that a user is circumventing,
but it is not impossible for a sufficiently powerful censor.
The problem doesn't exist when the front domain is one
that happens have its public key ``pinned'' in the headless browser,
for instance when using the Chrome extension and fronting through
\urll{www.google.com}.

@@
